Timeliness of security updates for Android and Chrome

### 2014-02-17 securityupdates.tex
Add some results from QInF

>>>>

The variation of the proportion of devices affected by a vulnerability with time tells us how bad a particular vulnerability affected the Android platform.
Figure \ref{fig:nvulnerabilities_heat} breaks this down by vulnerability to show how the proportion of devices affected by different vulnerabilities varies.
In 2013 three vulnerabilities were found in the way which Android verified the signatures on APKs.
These allowed the creation of malicious APKs which appear to be signed as system APKs -- which have root equivalent privileges.
Figure \ref{fig:nvulnerabilities_heat} shows how the the \emph{APK signing vulnerabilities} affected all devices and took months to get fixed for any device.
However what is perhaps more worrying is the long tail on the \emph{Gingerbreak}, \emph{levitator} and \emph{exploid} vulnerabilities which are more dangerous root exploits (not requiring new APK installation) and which still affect a significant proportion of devices years later.

\begin{figure}
 \includegraphics[width=0.5\textwidth]{figures/nvulnerabilities_heat.pdf}
 \caption{Proportion of devices affected by different vulnerabilities}
 \label{fig:nvulnerabilities_heat}
\end{figure}
\begin{figure}
 \includegraphics[width=0.5\textwidth]{figures/from_to_updates.pdf}
 \caption{Updates between different Android versions in the DA data}
 \label{fig:from_to_updates}
\end{figure}
\begin{figure}
 \includegraphics[width=0.5\textwidth]{figures/w_security_updates.pdf}
 \caption{Number of updates each week which fixed or may have fixed security vulnerabilities}
 \label{fig:weekly_security_updates}
\end{figure}
Figure \ref{fig:from_to_updates} shows how devices upgrade between different versions of Android.
Device Analyzer (DA) observes upgrade events and the figure shows which versions a device is upgrading from and to.
Mostly the dark cells are above the diagonal and are upgrades.
While many upgrades are from one version to the next version there are also a fair number which skip a few versions.
Surprisingly there are also a small number of downgrade events when older versions of Android are installed on to devices.
Figure \ref{fig:weekly_security_updates} shows the number of devices getting security updates each week, blue shows updates which changed the Android version number from a version with known vulnerabilities to one which had fewer known vulnerabilities.
Red indicates updates which changed the build number but not the version number and so might contain a backported fix for a vulnerability.
